%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{comment}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://users.soe.ucsc.edu/~waiting/}{\Large Weiting Zhan}} & Email : \href{mailto:zhanweiting2019@gmail.com}{zhanweiting2019@gmail.com}\\
  \href{https://users.soe.ucsc.edu/~waiting/}{Homepage:https://users.soe.ucsc.edu/~waiting/} & Mobile : +1-831-818-5593 \\
  \href{https://github.com/WaitingZhan/}{Git-hub :https://github.com/WaitingZhan/} &  \href{https://www.linkedin.com/in/weiting-zhan-ba482892//}{Linkedin:https://www.linkedin.com/in/weiting-zhan-ba482892/}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Califronia, Santa Cruz}{Santa Cruz, CA}
      {Master of Science in Computer Engineer}{Sep. 2017 -- Jun. 2019}
    \resumeSubheading
      {University of Chinese Academy of Sciences}{Shanghai, China}
      {Master of Engineering in Material Science}{Sep. 2013 -- Jun. 2017}
    \resumeSubheading
      {Shanghai University}{Shanghai, China}
      {Master of Science in Physics}{Sep. 2013 -- Jun. 2017}
    \resumeSubheading
    {Nanjin Tech University}{Nanjing, China}
      {Bachelor of Science in Chemistry}{Sep. 2008 -- Jun. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IOS Development}{Santa Cruz, CA}
      {Software Engineer}{Oct 2018 - Present}
      \resumeItemListStart
        \resumeItem{ISee}
          {Using Firebase MLKit API build an application for blind or visually impaired users. ISee read text and item in a image for blind user. \textbf{swift}}
        \resumeItem{Ballet Terms Dictionary}
          {Offer sound and image for each ballet Terms. \textbf{swift}}
      \resumeItemListEnd
      
    \resumeSubheading
      {Android Development}{Santa Cruz, CA}
      {Software Engineer}{Oct 2018 - Present}
      \resumeItemListStart
        \resumeItem{ISee}
          {Using Firebase MLKit API build an application for blind or visually impaired users. ISee read text and item in a image for blind user. \textbf{Java}}
      \resumeItemListEnd

    \resumeSubheading
      {Web Development}{Santa Cruz, CA}
      {Software Engineer}{Sep 2018 - Present}
        \resumeItemListStart
        \resumeItem{ISee}
          {Using Firebase MLKit API build an application for blind or visually impaired users on web. ISee read text and item in a image for blind user. \textbf{HTML, CSS, MySQL, PHP, jQuery and AJAX}}
      \resumeItemListEnd
    \resumeSubheading
      {Natural language processing}{Santa Cruz,CA}
      {Software Engineer}{Sep 2017 - Jun 2019}
      \resumeItemListStart
        \resumeItem{Tweeter Classifier}
          {Train a classifier to classify Trump and Hillary's tweeter.  \textbf{Python,Tensor Flow}}
        \resumeItem{Email Classifier}
          {Train a classifier to classify Spam/ham of email. \textbf{Python,Tensor Flow, sklearn, keras}}
        \resumeItem{Chat bot}
          {Build a chat bot using sequence to sequence model. \textbf{Python, Tensor Flow,GPU}}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Vision Project}{Santa Cruz, CA}
      {Research Assistant}{Jan 2017 - Jun 2019}
      \resumeItemListStart
        \resumeItem{High dynamic range imaging}
          {Heighten a picture’s dynamic range by combining 2 different exposure time pictures. \textbf{Python, OpenCV}}
        \resumeItem{Plane sweeping stereo}
          {Calculate homography of  2 images, Warp the image using the homography. Compute the depth for each pixel. \textbf{Python, OpenCV}}
        \resumeItem{Optical character recognition}
          {Evaluate the performance of Firebase MLKit with Blur Text Spot  \textbf{Python, OpenCV, Java, GPU}}
      \resumeItemListEnd
      

     \resumeSubheading
      {Network protocol simulation}{Santa Cruz, CA}
      {Software Engineer}{Oct 2018 - Apr 2019}
      \resumeItemListStart
        \resumeItem{Slotted ALOHA  Protocol Simulation}
          { Calculate the throughput of slotted ALOHA Protocol.\textbf{C++, NS3, Linux}}
        \resumeItem{Chord and Space Shuffle Implementation}
          {\textbf{Python}}
      \resumeItemListEnd
      

  \resumeSubHeadingListEnd
%-------------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Java, c++,Javascript, swift, HTML, CSS, MySQL, PHP, jQuery, AJAX}
    }
  \resumeSubHeadingListEnd

\end{document}
